Visually pleasing knot projections

### 2022-06-08 inst/jma_rebuttal_review3.tex

Page 3 line 42: ``...knots possess a line of symmetry (at least, the
diagrams do if the breaks are ignored), which ..."  -$>>$ ``...knots
possess a C2 rotation axis, which ..."

Page 4 lines 22-25: ``One plausible technique for creating knot
projections is to consider a two-dimensional projection of a knot's
embedding E in R3. However, this approach often results in poor visual
appearance: cusps or other displeasing effects can occur."  -$>>$ True!
- But what is the alternative, if the user has an entangled physical
knot in her hands?

Page 4 line 45: Define ``nodes" !

\textcolor{blue}{``Nodes'' is a standard word in the context of Bezier
  curves. I have not used the word in any other sense in the
  manuscript and I think the text is clear as it stands.}

@@

I am missing a description how the two breaks at every crossing point
are being graphically implemented.

Conclusions:

RE: ``Further work might include functionality to deal
with links."  $>>$ Readers may think that this would be a trivial
extension.  Please add a paragraph like the one you wrote in response
to Reviewer 1, to explain why the extension to links may be more
difficult than one might think.

\textcolor{blue}{Done, new subsection ``some reflections on links''
  at the end, under ``conclusions and further work''}

### 2022-06-08 inst/jma_knot.tex
fixes #71

The {\tt knotR} package allows the user to create rough diagrams of
knots using the inkscape suite of software, and subsequently polish up
such diagrams in terms of a customizable objective function using
numerical optimization techniques.  Further work might include
functionality to deal with links.  In the broader context of
optimisation in art, we observe that numerical optimisation techniques
can produce aesthetically pleasing results, an observation that might
find uptake by graphic artists.

>>>>

The {\tt knotR} package allows the user to create rough diagrams of
knots using the inkscape suite of software, and subsequently polish up
such diagrams in terms of a customizable objective function using
numerical optimization techniques.

In the broader context of optimisation in art, we observe that
numerical optimisation techniques can produce aesthetically pleasing
results, an observation that might find uptake by graphic artists.

\subsection{Some reflections on links}

Further work might include functionality to deal with links.  Much of
the required functionality is (in principle) already present in the
software.  Each component would have its own badness, and in addition
there would be $n(n-1)/2$ inter-component interaction terms measuring
features such as closeness between non-intersecting strands of
different components.  However, the implementation of such
functionality is not straightforward and several problems stand out.
Firstly, dealing with inter-component intersection points is
difficult.  Currently, crossing points are represented as a
(symmetrical) Boolean matrix with rows and columns corresponding to
strands, and entry $(i,j)$ being whether strand $i$ intersects with
strand $j$.  The link generalization would be a symmetric matrix with
entries that are themselves intersection matrices: an object with four
indices and entry $(i,j,k,l)$ indicating whether strand $j$ of
component $i$ intersects strand $l$ of component $k$.  Such objects
are unwieldy to work with and are typically difficult to manipulate.
Secondly, the imposition of symmetry is not straightforward in the
case of links: one might desire that certain components of a link have
a particular kind of symmetry and others to have a different kind (or
no!) symmetry.  Further, one unexpectedly difficult problem was
dealing with a subset of components that individually possess no
symmetry but collectively possess mirror (or rotational) symmetry.
Even the simplest links, as in Figure~\ref{thistlethwaite}, can be
problematic.  Consider Thistlethwaite's L4a1, for example: one would
expect the two components to be identical except for a 90-degree
rotation, and implementing this in the context of the package does not
seem to be at all easy.  In general, new badnesses would be needed.
Further, in L7a1, the smaller component should be not only as circular
as possible (?), but also one might desire the overall length to be
smaller than that of the other component.  It would be reasonable to
conclude that dealing with links might be possible in principle but,
due to a number of technical and mathematical reasons, considerably
harder than the single-component links considered here.

\begin{figure}[htbp]
  \begin{center}
\includegraphics[width=7cm]{L4a1_L7a1}  % made by exporting L4a1_L7a1.svg as PDF
\caption{Two links \label{thistlethwaite} taken from the
  Thistlethwaite link table~\cite{hoste1998}.  These are produced
  directly with inkscape and are not optimized}
  \end{center}
\end{figure}
